The Astropy Project: \\ Sustaining and Growing a Community-oriented Open-source Project and the Latest Major Release (v5.0) of the Core Package

### 2022-01-20 src/ms.tex
add initial learn text

\begin{itemize}
\item Current status and scope
\item Vision for the future (review what we said in v2.0 paper)
\item User forums and engagement with user base
\item Workshops
\end{itemize}

>>>>

\subsubsection{Current status and scope}

The Astropy-ii paper discussed the {\it Learn Astropy} effort only in the
context of online tutorials and guides. This vision has been realized as
{\it Learn Astropy} has released a new version of this website, and has
expanded its efforts
in user engagement and in conducting workshops. The Learn team meets
weekly to drive these issues forward.

\begin{itemize}

\item {\bf Learn Astropy website:} The site has a new search interface powered by
Algolia which is used by major shopping sites. This work has been
supported in part by the Dunlap grant. Tutorials have been added and
a {\it ccdproc} Jupyter book has been completed.

\item {\bf User forums:} In addition to the pre-existing Astropy mailing list,
and the Python in Astronomy Facebook group, users have been invited to the
Astropy Slack workspace. The Moore Foundation grant allows this Slack space to
be on a paid plan; additionally NumFOCUS has negotiated a special rate for
open-source projets. There is some internal debate amongst Astropy developers
on whether Astropy Slack should be reserved for developer discussions, with
users redirected to another site. Accordingly, the Astropy Project has commissioned
a Discourse site which is more open than the Facebook group and more user-oriented
than Astropy Slack. A benefit of the Moore Foundation grant is that Astropy
developers are able to invoice as independent contractors the time they
spend helping users on these forums.

\item {\bf Workshops:} the Project has been conducting workshops at winter meetings
of the American Astronomical Society since AAS 225 in January 2015. Up to the
start of the coronavirus pandemic, these were full-day in-person workshops with
as many as 90 participants and a dozen facilitators from the project. During the
pandemic, these workshops were moved to an online format and split into
basic and advanced sessions. Additionally, beginning with the AAS 238 online
meeting, the workshops have been expanded to Summer AAS meetings. The Learn
team finds that the workshop audience is best found as AAS meetings as opposed
to more general Python meetings.

\end{itemize}

\subsubsection{Learn vision for the future}

The Learn plan going forward is to continue to improve the tutorial website;
to index third-party tutorials; to promote user engagement on the Discourse
site; and to look for supportable opportunities to expand the reach of
Astropy workshops beyond the American Astronomical Society meetings.
